---
title: "p548_final"
author: "Rafeel Wasif"
date: "March 14, 2017"
output: html_document
---

```{r}

library(dplyr)
library( rjags )


```



```{r}
data.ini = c(
   0, 133, 132, 124, 118, 64.5, 816932,
   1, 140, 150, 124, -9, 72.5, 1001121,
   1, 139, 123, 150, 143, 73.3, 1038437,
   1, 133, 129, 128, 172, 68.8, 965353,
   0, 137, 132, 134, 147, 65.0, 951545,
   0, 99, 90, 110, 146, 69.0, 928799,
   0, 138, 136, 131, 138, 64.5, 991305,
   0, 92, 90, 98, 175, 66.0, 854258,
   1, 89, 93, 84, 134, 66.3, 904858,
   1, 133, 114, 147, 172, 68.8, 955466,
   0, 132, 129, 124, 118, 64.5, 833868,
   1, 141, 150, 128, 151, 70.0, 1079549,
   1, 135, 129, 124, 155, 69.0, 924059,
   0, 140, 120, 147, 155, 70.5, 856472,
   0, 96, 100, 90, 146, 66.0, 878897,
   0, 83, 71, 96, 135, 68.0, 865363,
   0, 132, 132, 120, 127, 68.5, 852244,
   1, 100, 96, 102, 178, 73.5, 945088,
   0, 101, 112, 84, 136, 66.3, 808020,
   1, 80, 77, 86, 180, 70.0, 889083,
   1, 83, 83, 86, -9, -9, 892420,
   1, 97, 107, 84, 186, 76.5, 905940,
   0, 135, 129, 134, 122, 62.0, 790619,
   1, 139, 145, 128, 132, 68.0, 955003,
   0, 91, 86, 102, 114, 63.0, 831772,
   1, 141, 145, 131, 171, 72.0, 935494,
   0, 85, 90, 84, 140, 68.0, 798612,
   1, 103, 96, 110, 187, 77.0, 1062462,
   0, 77, 83, 72, 106, 63.0, 793549,
   0, 130, 126, 124, 159, 66.5, 866662,
   0, 133, 126, 132, 127, 62.5, 857782,
   1, 144, 145, 137, 191, 67.0, 949589,
   1, 103, 96, 110, 192, 75.5, 997925,
   1, 90, 96, 86, 181, 69.0, 879987,
   0, 83, 90, 81, 143, 66.5, 834344,
   0, 133, 129, 128, 153, 66.5, 948066,
   1, 140, 150, 124, 144, 70.5, 949395,
   0, 88, 86, 94, 139, 64.5, 893983,
   1, 81, 90, 74, 148, 74.0, 930016,
   1, 89, 91, 89, 179, 75.5, 935863 )

data.2 = ifelse( data.ini == -9, NA, data.ini )

brain.mat = matrix( data.2, ncol = 7, byrow = T )

dimnames(brain.mat) = list( NULL, 
         c("code.ini", "fsiq", "viq", "piq", 
            "weight", "height", "mri.cnt") )

brain.mat = brain.mat[ order(brain.mat[,"code.ini"]), ]

# Create a factor variable for gender.
gen.char = ifelse(
                     brain.mat[,"code.ini"] == 0, "female", "male")

gender = factor(gen.char)

gen.code = as.numeric(gender)

brain.fm = data.frame( gender, gen.code, 
   brain.mat[ , c("fsiq", "viq", "piq", 
                        "weight", "height", "mri.cnt")] )





```

Separating the MALE Data.

```{r}
m.data <- filter(brain.fm, gender == "male")


```

Standardizing the data.

```{r}

m.data$mri.x = m.data$mri.cnt/10000



```

ScatterPlot

```{r}

plot(m.data$viq ~ m.data$mri.x, main="Scatterplot",
   xlab="VIQ ", ylab="MRI.X" )



```

Code for list of data, as well as model.


```{r,warning= FALSE, message=FALSE}

setwd("C:/Users/Rafeel/OneDrive/Documents/R-Work/kruschke.r")

getwd()
attach( "jmfuns.rda", pos = 2)

modelString.2 = "
# Standardized Variables Analysis:  In this analysis,
# the predictor and predicted variables are 
# transformed to z-scores.
# ---------------------------------------------------
# DATA TRANSFORMATION:  Standardize the data:
data {
   Ntotal <- length(y)
   xm <- mean(x)
   ym <- mean(y)
   xsd <- sd(x)
   ysd <- sd(y) 
   for ( i in 1:length(y) ) {
      zx[i] <- ( x[i] - xm ) / xsd
      zy[i] <- ( y[i] - ym ) / ysd
   }
}
# -------------------------------

# Specify the model for standardized variables:

model {

# Likelihood Function (non-central t):
 
   for ( i in 1:Ntotal ) {
      zy[i] ~ dt( zB0 + zB1 * zx[i] , 1/(zsigma^2), nu)
   }

   # Priors vague on the standardized scale:

   zB0         ~ dnorm( 0 , 1/(10)^2 )   
   zB1         ~ dnorm( 0 , 1/(10)^2 )

   zsigma      ~ dunif( 1.0E-3 , 1.0E+3 )

   nuMinusOne  ~ dexp(1/29.0)
   nu         <- nuMinusOne+1

   # Transform to original scale:
   B1 <- zB1 * ysd / xsd   
   B0 <- zB0 * ysd   + ym - zB1 * xm * ysd / xsd 

   sigma <- zsigma * ysd

}  # close bracket for model syntax

" # close quote for modelString.2

# Write out modelString.2 to a text file

writeLines( modelString.2 , con="regr.std.txt" )

# =============================================================== ====

# Table 11.  Specify settings for the JAGS run on the             ----
# standardized variables regression                               ----

# Specify the data in a list, for later shipment to JAGS:

dataStdVars = list(
x = m.data$mri.x, 
y = m.data$viq)

length(m.data$mri.x) == length(brain.fm$viq)
parameters = c(   "B0",  "B1",  "sigma", 
               "zB0", "zB1", "zsigma", "nu" )

adaptSteps = 1000  # Number of adaptation steps

burnInSteps = 1000

numSavedSteps = 50000

nChains = 2 

thinSteps = 1

nIter = ceiling((numSavedSteps*thinSteps) / nChains)
#     = 12500

# =============================================================== ====

# Table 12.  Use JAGS to compute the Bayesian linear regression   ----
# for the standardized variables                                  ----

stdVars.mod = jags.model(
               file     = "regr.std.txt",
               data     = dataStdVars, 
               n.chains = nChains,
               n.adapt  = adaptSteps,
               )

{cat( "Burning in the MCMC chain...\n" )
update( stdVars.mod, n.iter = burnInSteps )  }

{cat( "Sampling final MCMC chain(s) ...\n" )
mcmcCoda = coda.samples( 
                  model  = stdVars.mod, 
                  var    = parameters, 
                  n.iter = nIter, 
                  thin   = thinSteps )  }


```
# =============================================================== ====



Results for the Regression. We can say that the slope B[1] is not negligible as more than 95% values like outside the -0.05 and 0.05 region.

```{r}

mcmccoda.mat.reg <- as.matrix(mcmcCoda)
mcmccoda.df.reg <- as.data.frame(mcmccoda.mat.reg)

# Finding values of B[1] between -0.05 and 0.05.

res.param(mcmccoda.df.reg$B1, ROPE =  c(-0.05, 0.05 )) 


# For Finding the values of B[1] that lie beyond 0.05. 
length( which( mcmccoda.df.reg$B1 > 0.05))/length(mcmccoda.df.reg$`b[1]`) * 100
length( which( mcmccoda.df.reg$B1 < 0.05))/length(mcmccoda.df.reg$`b[1]`) * 100



```

Q2


```
```{r}
str(mcmcCoda)
mcmcCoda.matrix <- as.matrix(mcmcCoda)

summary(mcmcCoda)

```






```
23% of the difference values lie between -2 and 2 rope difference.

```{r}
setwd("C:/Users/Rafeel/OneDrive/Documents/R-Work/kruschke.r")


#graphics.off() # This closes all of R's graphics windows.
#rm(list=ls())  # Careful! This clears all of R's memory!
#------------------------------------------------------------------------------- 

myDataFrame = brain.fm
yName="viq" 
xName="gen.code" 
# Load the relevant model into R's working memory:
setwd("C:/Users/Rafeel/OneDrive/Documents/R-Work/kruschke.r")

source("Jags-Ymet-Xnom1fac-MnormalHom.R")
#------------------------------------------------------------------------------- 
# Generate the MCMC chain:
mcmcCoda = genMCMC( datFrm=myDataFrame , yName=yName , xName=xName ,
                    numSavedSteps=11000 , thinSteps=10)  #saveName=fileNameRoot )

summary(mcmcCoda)


```

24% values of dif lie between -2 and 2. 15% lie above 2 and 60% values lie below -2.



```{r}
# For Finding the values of B[1] that lie beyond 0.05. 


mcmccoda.mat <- as.matrix(mcmcCoda)
mcmccoda.df <- as.data.frame(mcmccoda.mat)
dif = mcmccoda.df$`m[1]` - mcmccoda.df$`m[2]`

# Rope between -2 and 2.

res.param(dif, ROPE =  c(-2, 2 )) 



# Rope less than -2 and greater than 2.
length( which( dif > 2))/length(dif) * 100
length( which( dif < -2))/length(dif) * 100



```

